Choose a License

### 2024-11-28 choose_license.qmd
Describe license situation for researchers at LMU

>>>>

::: {#nte-situation-lmu .callout-note collapse="true"}
### For researchers at LMU

If you are an employee at LMU and your funder does not mandate the use of a particular license, the decision which license to use lies with your associated chair. In the (rare) case the software you developed has a technical application and constitutes an invention, you are required to officially report your invention to the university which decides on its release. If the university claims the invention, you may not apply a copyright license that makes a patent grant. More information about this process is provided in the [service portal](https://www.serviceportal.verwaltung.uni-muenchen.de/internationals/research_transfer/intellectual_property/index.html). More information about software patents are provided by the FSFE: [Software Patents in Europe](https://fsfe.org/activities/swpat/swpat.en.html).
:::
